\documentclass[11pt]{article}

% Compact layout with reduced margins
\usepackage[letterpaper, margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{array}
\usepackage{parskip}

% Optional font packages
\usepackage{tgpagella}  % Palatino-like font

% Color definitions
\definecolor{accent}{RGB}{51, 105, 173}  % Deeper blue
\definecolor{linkcolor}{RGB}{0, 0, 120}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    pdfauthor={Ranjit Kumaresan}
}

% Custom section format - more compact
\titleformat{\section}
{\large\bfseries\color{accent}}
{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}

% Remove page numbers
\pagestyle{empty}

% Custom commands
\newcommand{\entry}[4]{
    \noindent\textbf{#1} \hfill \textit{#2} \\
    \noindent\textit{#3} \hfill #4 \\
}

\newcommand{\entryshort}[2]{
    \noindent\textbf{#1} \hfill #2 \\
}

\usepackage{fontawesome}

\begin{document}

% Header - more elegant layout
\begin{center}
    \LARGE\textbf{Ranjit Kumaresan} \\
    \vspace{1mm}
    \normalsize
    43767 Paso Nuez Cmn, Fremont CA 94539 \quad
    \faPhone\ 617-335-9993 \quad 
    \faEnvelope\ \href{mailto:vranjit@gmail.com}{vranjit@gmail.com} \\
    \faGlobe\ \href{http://people.csail.mit.edu/ranjit/}{Academic webpage} \quad
    \faGoogle\ \href{https://scholar.google.com/citations?user=YC3Ab4oAAAAJ&hl=en}{Google Scholar} \quad
    \faDatabase\ \href{https://dblp.org/pid/14/4245.html}{DBLP}
\end{center}

\vspace{-3mm}

% Research Interests
\section{Research Interests}
Fundamental aspects of cryptography with applications to various technologies including AI and blockchain.

% Education - fixed spacing
\section{Education}
\entry{University of Maryland}{2006 – 2012}{M.S. and Ph.D. in Computer Science}{College Park, MD}
\entry{Indian Institute of Technology}{2002 – 2006}{B.Tech in Computer Science}{Chennai, India}

\vspace{-5mm}

% Work Experience - condensed
\section{Professional Experience}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item \textbf{Visa Research}, Palo Alto, CA — Research Scientist (2018 – Present)
    \item \textbf{Microsoft Research}, Redmond, WA — Researcher, Cryptography Group (2016 – 2018)
    \item \textbf{Massachusetts Institute of Technology}, Cambridge, MA — Postdoctoral Associate (2015 – 2016)
    \item \textbf{Technion—Israel Institute of Technology}, Haifa, Israel — Postdoctoral Research Scholar (2012 – 2014)
\end{itemize}

% Select Patents (shortened)
\section{Selected Patents}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item R. Kumaresan, S. Raghuraman, and R. Sinha. ``System and computer program product for fair, secure n-party computation using at least one blockchain.'' US Patent 12261955.
    \item R. Kumaresan, M. Zamani, S. Raghuraman, M. Christodorescu, M. Minaei. ``Conditional offline interaction system and method.'' US Patent 12238209.
    \item R. Sinha, R. Kumaresan, S. Gaddam, M. Christodorescu, S. Raghuraman. ``System, method, and computer program product for secure real-time N-party computation.'' US Patent 12081677.
    \item M. Minaei, R. Kumaresan, M. Zamani, S. Gaddam. ``Universal payment channels.'' US Patent 11995623.
    \item V. Kolesnikov and R. Kumaresan. ``Secure Function Evaluation For A Covert Client And A Semi-Honest Server Using String Selection Oblivious Transfer.'' U.S. Patent 8990570.
\end{itemize}

% Recent Publications (most recent publications only)
\section{Recent Conference Publications}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item M. Minaei, P. Moreno-Sanchez, Z. Fang, S. Raghuraman, N. Alamati, P. Chatzigiannis, R. Kumaresan, D. Le. ``DTL: Data Tumbling Layer. A Composable Unlinkability for Smart Contracts.'' \textit{AsiaCCS 2025.}
    \item L. Ng, P. Chatzigiannis, D. Le, M. Minaei, R. Kumaresan, M. Zamani. ``A Plug-and-Play Long-Range Defense System for Proof-of-Stake Blockchains.'' \textit{ESORICS 2024.}
    \item R. Kumaresan, D. Le, M. Minaei, S. Raghuraman, Y. Yang, M. Zamani. ``Programmable Payment Channels.'' \textit{ACNS 2024}.
    \item M. Minaei, P. Chatzigiannis, S. Jin, S. Raghuraman, R. Kumaresan, M. Zamani, P. Moreno-Sanchez. ``Unlinkability and Interoperability in Account-Based Universal Payment Channels.'' \textit{Financial Cryptography Workshop 2023}.
    \item R. Kumaresan, S. Raghuraman, A. Sealfon. ``Synchronizable Fair Exchange.'' \textit{Theory of Cryptography Conference 2023}.
    \item S. Gaddam, R. Kumaresan, S. Raghuraman, R. Sinha. ``LucidiTEE: Scalable policy-based multiparty computation with fairness.'' \textit{CANS 2023}.
    \item S. Badrinarayanan, R. Kumaresan, M. Christodorescu, V. Nagaraja, K. Patel, S. Raghuraman, P. Rindal, W. Sun, M. Xu. ``A plug-n-play framework for scaling private set intersection to billion-sized sets.'' \textit{CANS 2023}.
\end{itemize}

\section{Selected Earlier Publications}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item A. Miller, I. Bentov, S. Bakshi, R. Kumaresan, and P. McCorry. ``Sprites and State Channels: Payment Networks that Go Faster Than Lightning.'' \textit{Financial Cryptography 2019.}
    \item I. Bentov, R. Kumaresan, and A. Miller. ``Instantaneous Decentralized Poker.'' \textit{Advances in Cryptology—Asiacrypt 2017.}
    \item R. Kumaresan and I. Bentov. ``Amortizing Secure Computation with Penalties.'' \textit{Proc. 23rd ACM Conf. on Computer and Communications Security (CCS) 2016}.
    \item R. Kumaresan, V. Vaikuntanathan, and P. Vasudevan. ``Improvements to Secure Computation with Penalties.'' \textit{Proc. 23rd ACM Conf. on Computer and Communications Security (CCS) 2016}.
    \item V. Kolesnikov, R. Kumaresan, M. Rosulek, and N. Trieu. ``Efficient Batched Oblivious PRF with Applications to Private Set Intersection.'' \textit{Proc. 23rd ACM Conf. on Computer and Communications Security (CCS) 2016}.
    \item R. Kumaresan, S. Raghuraman, and A. Sealfon. ``Network Oblivious Transfer.'' \textit{Advances in Cryptology—Crypto 2016}.
    \item R. Kumaresan, T. Moran, and I. Bentov. ``How to Use Bitcoin to Play Decentralized Poker.'' \textit{Proc. 22nd ACM Conf. on Computer and Communications Security (CCS) 2015}.
    \item R. Kumaresan and I. Bentov. ``How to Use Bitcoin to Incentivize Correct Computations.'' \textit{Proc. 21st ACM Conf. on Computer and Communications Security (CCS) 2014}.
    \item I. Bentov and R. Kumaresan. ``How to Use Bitcoin to Design Fair Protocols.'' \textit{Advances in Cryptology—Crypto 2014}.
    \item A. Beimel, Y. Ishai, R. Kumaresan, and E. Kushilevitz. ``On the Cryptographic Complexity of the Worst Functions.'' \textit{11th Theory of Cryptography Conference (TCC) 2014}.
    \item V. Kolesnikov and R. Kumaresan. ``Improved OT Extension for Transferring Short Secrets.'' \textit{Advances in Cryptology—Crypto 2013}.
    \item S.G. Choi, J. Katz, R. Kumaresan, and H.-S. Zhou. ``On the Security of the 'Free-XOR' Technique.'' \textit{9th Theory of Cryptography Conference (TCC) 2012}.
    \item J.A. Garay, J. Katz, R. Kumaresan, and H.-S. Zhou. ``Adaptively Secure Broadcast, Revisited.'' \textit{ACM Symposium on Principles of Distributed Computing (PODC) 2011}.
    \item R. Kumaresan, A. Patra, C.P. Rangan. ``The Round Complexity of Verifiable Secret Sharing: The Statistical Case.'' \textit{Advances in Cryptology—Asiacrypt 2010}.
    \item J. Katz, C.-Y. Koo, and R. Kumaresan. ``Improving the Round Complexity of VSS in Point-to-Point Networks.'' \textit{Intl. Colloquium on Automata, Languages and Programming (ICALP) 2008}.
\end{itemize}

\section{Selected Preprints and Technical Whitepapers}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item R. Kumaresan. ``Improved Garbled Circuit Lookup Tables.'' (Under Submission)
    \item R. Kumaresan. ``Improved Pseudorandom Error-Correcting Codes and Application to Watermarking LLM Outputs.'' (Under Submission)
    \item M. Minaei, D. Le, R. Kumaresan, A. Beams, P. Moreno-Sanchez, Y. Yang, S. Raghuraman, P. Chatzigiannis, M. Zamani. ``Scalable Off-Chain Auctions.'' ePrint 2023/1454.
    \item S. Gaddam, R. Kumaresan, S. Raghuraman, R. Sinha. ``How to Design Fair Protocols in the Multi-Blockchain Setting.'' ePrint 2023/762.
    \item R. Kumaresan. ``Method and system to automatically synthesize smart contracts using transaction traces.'' Technical Disclosure Commons 2023.
    \item M. Christodorescu, E. English, W. Gu, D. Kreissman, R. Kumaresan, M. Minaei, S. Raghuraman, C. Sheffield, A. Wijeyekoon, M. Zamani. ``Universal Payment Channels: An Interoperability Platform for Digital Currencies.'' CoRR abs/2109.12194 (2021).
\end{itemize}

\section{Professional Service}
\textbf{Program Committee Member:} ACM CCS 2023; Eurocrypt 2017; ACM CCS 2016; ICITS 2016; SCN 2016; ACNS 2015

\textbf{External Reviewer:} Journal of Cryptology, Algorithmica, STOC, Crypto, Eurocrypt, Asiacrypt, CCS, TCC, PODC, DISC (various years)

\end{document}